% NOTE:
% "project" should be a custom environment to be used for a single project, internship, etc.
% The specifications of that environment should be as follows:
% First argument is an OPTIONAL link
% Second argument is the name of the project
% Third argument is the date/duration
% Fourth argument is the name of the mentor(s)

\section*{Internships}
\begin{itemize}

\item \begin{project}{Retrieval-based Chat Bot}{May '19 - Present}{ EJET Systems, ML and NLP}
	\item Handled full development of a hotel assistant bot.
    \item Built a Food Entity Recognition model to identify food items in a sentence, along with quantity, attribute, and toppings using NLTK.
    \item Built Food Recommendation model using word embedding and also devised an algorithm to recommend food with respect to multiple food items.
    \item Developed a binary sentimental analysis model using word embedding and classification using random forest classifier.
    \item Researched robust image hashes that are immune to typical image transformations, while being sensitive to malicious image edits such as face swaps, deep fakes, object addition/deletion.
    \item Constructed models that take an image and output a binary hash that would give lower \href{https://en.wikipedia.org/wiki/Hamming\_distance}{\textit{Hamming distances}} for hashes of similar images while giving more considerable distances for dissimilar images.
    \item Developed a \textit{framework} for testing against transformations like compression, contrast changes, blurring, warping.
    \item Trained various novel network architectures on the \href{https://dl.acm.org/citation.cfm?id=1756042}{\textit{triplet loss}} along with \href{https://arxiv.org/abs/1503.03832}{\textit{mining}} of examples for improved training.
    \item Tested the networks against \textit{adversarial attack} methods such as \href{https://arxiv.org/abs/1412.6572}{\textit{FGSM}}, \href{https://arxiv.org/abs/1706.06083}{\textit{Projected Gradient Descent}}.
\end{project}

\end{itemize}
