% NOTE:
% "project" should be a custom environment to be used for a single project, internship, etc.
% "emptyproject" should be a custom command to be used for an empty listing for a single project, internship, etc.
% The specifications of both of the above should be as follows:
% First argument is an OPTIONAL link
% Second argument is the name of the project
% Third argument is the date/duration
% Fourth argument is the name of the mentor(s)

\section*{Projects}
\begin{itemize}

\item \begin{project}[\faGithub  https://github.com/hitesh-gupta-2111/FIR-Management-System]{FIR Management System}{Jan '19 - Apr '19}{Prof. Arnab Bhattacharya}
    \item Designed a FIR management system by using Apache, MySQL, PHP.
\end{project}

\item \begin{project}[]{GeoInformatics Project}{Aug '18 - Dec '18}{Prof. Salil Goel, CE331A Course Project}
	\item Used instruments like Auto-level, GPS, Total station for collecting data of given site.
    \item Used QGIS software for making Map from collected data.
\end{project}

\item \begin{project}[]{Project on Structural Stability}{Summer '18}{Prof. Suparno Mukhopadhyay}
	\item Analysed structures for their stability and strength using MATLAB.
\end{project}

\item \begin{project}[]{Crude Oil Pump}{Jan '18 - Apr '18}{Course Project, TA201A}
	\item Designed (in AutoCAD), manufactured and assembled a small model of a crude oil pump.
    \item Used techniques like welding, brazing and bending to fabricate the model.
\end{project}

\item \begin{project}[]{Rice Huller Machine}{Aug '17 - Nov '17}{Course Project, TA202A}
	\item A small machine which can be used at home easily to remove husk.
    \item Designed (in AutoCAD), manufactured and assembled a mechanism to remove the husk of rice in which the grain is crushed by two rubber coted rollers. Used machining techniques like lathing, milling, drilling to fabricate the model.
\end{project}

\end{itemize}
